### 2019-01-21 journal/localizations.tex
fix localize

\subsection{Coverage-Based Localizaton}

By definition, when a mutant repairs a test case, it changes the
behavior of the test.  In some cases, this behavioral change is
limited to changes in program state and data values.  However, the
vast majority of mutant repairs also modify the code coverage of a
test; in our experiments, there were no repairs that did not change
coverage.  If a fault can be avoided by, for example, disabling a
problematic optimization in a compiler, this naturally leads to
changed coverage.  If the fault is due to a bad conditional, where a
program path should include additional code, the repair will often
change the execution to include the omitted code.  As a localization
for a fault, then, we can examine the source statements whose
  coverage changed most often in repairs.  Early experiments with this
  approach showed that a useful coverage change localization must  account for the frequency of a
change.  Some coverage changes are extremely common across all
failures, faults, and repairing mutants,
and therefore likely not related to any specific fault.

\begin{quote}
The {\bf Coverage} localization for a failing test case $f \in F$ ($F$
is the set of all failing test cases) ranks
statements by the function $r$ (for rank) where:
%$$U = s : \forall m . \forall t \in F . c(m,t,s) = 1$$
$$C(s) = \sum_{t \in F} (\sum_{m \in R(t)} c(m,t,s))$$
%\[
$$r(s,f) = \sum_{m \in R(f)}\frac{1}{C(s)}c(m,f,s)$$
%\begin{cases}
% \sum_{m \in R(f)}\frac{1}{C(s)}c(m,f,s) & s \not\in U\\
%   0 & s \in U
%\end{cases}
%\]
$c(m,t,s)$ is 1 if coverage of $s$ changes for test $t$
with mutant $m$, and 0 otherwise.  $R(f)$ is the set of mutants repairing $f$.
\end{quote}

That is, the ranking is based on the number of times a statement's
coverage changes its value (covered or not covered) from the original
execution of $f$ in executions of mutants that repair $f$.  Changes are weighted by their inverse frequency over all
failures and all mutants.
Higher values for $r$ result in a higher ranking (more likely to
be faulty).

The coverage localization also provides a kind of explanation, though
a less direct one.  For any
interesting line of code in the coverage-change-based localization,
the user can investigate a particular instance of the change,
by selecting a single mutant and stepping through the execution of the
failing test case in a debugger to the point of change.  The user can also
browse through all mutants that produce this coverage change for the test
case.

@@

>>>>

@@

%\subsection{Coverage-Based Localizaton}
